Visualizing the Independence Problem Using Extended Association and Mosaic Plots

### 2003-03-08 trunk/vcd/paper/draft.Rnw
*** empty log message ***
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@218 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
*** empty log message ***
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@219 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{figure}[htbp]
\begin{center}
<<goals-assoc-classic,fig=TRUE,echo=FALSE,height=5,width=5>>=
grid.assocplot(goals, rot = 0)
@
\caption{Association plot for the Bundesliga data.}
\label{fig:goals-assoc-classic}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<goals-mosaic-classic,fig=TRUE,echo=FALSE,height=5,width=5>>=
mosaicplot(t(goals), shade = TRUE, main = "")
@
\caption{Friendly mosaic plot for the Bundesliga data.}
\label{fig:goals-mosaic-classic}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<goals-assoc-signif,fig=TRUE,echo=FALSE,height=5,width=5>>=
grid.assocplot(goals, color = "signif", rot = 0)
@
\caption{Extended association plots for the Bundesliga data.}
\label{fig:goals-assoc-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<haireye-assoc-signif,fig=TRUE,echo=FALSE,height=5,width=5>>=
grid.assocplot(haireye, color = "signif")
@
\caption{Extended association plots for the Hair-Eye-Color data.}
\label{fig:haireye-assoc-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<goals-mosaic-signif,fig=TRUE,echo=FALSE,height=5,width=5>>=
grid.mosaicplot(goals, main = NULL)
@
<<haireye-mosaic-signif,fig=TRUE,echo=FALSE,height=5,width=5>>=
grid.mosaicplot(haireye, main = NULL)
@
\caption{Extended mosaic plots for the Bundesliga and Hair-Eye-Color data.}
\label{fig:both-mosaic-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-assoc-signif,fig=TRUE,echo=FALSE,height=5,width=5>>=
tabplot(UCBAdmissions, color = "signif")
@
\caption{Extended conditioned association plots for the UCB Admissions data.}
\label{fig:UCB-assoc-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-mosaic-signif,fig=TRUE,echo=FALSE,height=5,width=5>>=
grid.mosaicpairs(UCBAdmissions, type = "conditional")
@
\caption{Extended conditioned association plots for the UCB Admissions data.}
\label{fig:UCB-mosaic-signif}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
<<goals-assoc-classic,fig=TRUE,echo=FALSE,height=6,width=6>>=
grid.assocplot(goals, rot = 0, gp = gp.binary)
@
\caption{Association plot for the Bundesliga data.}
\label{fig:goals-assoc-classic}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<goals-mosaic-classic,fig=TRUE,echo=FALSE,height=6,width=6>>=
mosaicplot(t(goals), shade = TRUE, main = "")
@
\caption{Friendly mosaic plot for the Bundesliga data.}
\label{fig:goals-mosaic-classic}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<goals-assoc-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
grid.assocplot(goals, rot = 0)
@
\caption{Extended association plots for the Bundesliga data.}
\label{fig:goals-assoc-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<haireye-assoc-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
grid.assocplot(haireye)
@
\caption{Extended association plots for the Hair-Eye-Color data.}
\label{fig:haireye-assoc-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<goals-mosaic-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
grid.mosaicplot(goals, main = NULL)
@
<<haireye-mosaic-signif,fig=TRUE,echo=FALSE,height=6,width=6>>=
grid.mosaicplot(haireye, main = NULL)
@
\caption{Extended mosaic plots for the Bundesliga and Hair-Eye-Color data.}
\label{fig:both-mosaic-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-assoc-signif,fig=TRUE,echo=FALSE,height=10,width=10>>=
tabplot(UCBAdmissions)
@
\caption{Extended conditioned association plots for the UCB Admissions data.}
\label{fig:UCB-assoc-signif}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<UCB-mosaic-signif,fig=TRUE,echo=FALSE,height=8,width=8>>=
grid.mosaicpairs(UCBAdmissions, type = "conditional", main = NULL)
@
\caption{Extended conditioned association plots for the UCB Admissions data.}
\label{fig:UCB-mosaic-signif}
\end{center}
\end{figure}
